---
title: "lab1"
author: "Brian Panjaitan"
date: "13/01/2020"
output: html_document
---

1 Getting Started
```{r}
getwd()

a = 2+2
a

(answer = 4-3*5+3*(1+2))

w <- 2
w = 1; (w <- 2)
w = 1; (w < -2)

radius = 4
volume = 4/3*pi*radius^3

radius = c(1,3,5,7)
volume = 4/3*pi*radius^3

plot(radius, volume, main = "title", xlab = "xlabel", ylab = "ylabel", ylim = c(0,1500), xlim = c(-1,9))
```

Problem 1
```{r}
radius = seq(1, 7, by = 2)
volume = 4/3*pi*radius^3

par(mfrow = c(2,2))
plot(radius, volume, main = "Sphere's Radius & Volume \n using Lines", xlab = "Radius of Sphere", ylab = "Volume of Sphere", type = "l")
plot(radius, volume, main = "Sphere's Radius & Volume \n using Points", xlab = "Radius of Sphere", ylab = "Volume of Sphere", type = "p")
plot(radius, volume, main = "Sphere's Radius & Volume \n using Nothing", xlab = "Radius of Sphere", ylab = "Volume of Sphere", type = "n")
plot(radius, volume, main = "Sphere's Radius & Volume \n using Both Lines and Points", xlab = "Radius of Sphere", ylab = "Volume of Sphere", type = "b")
```

Problem 2
```{r}
rad = seq(1,10000)
volume = 4/3*pi*rad^3

plot(rad, volume, main = "Plot of a Sphere's \n Radius vs Volume using Lines (Radius = 10,000)", xlab = "Radius of Sphere", ylab = "Volume of Sphere")
```

Problem 3
```{r}
x = seq(1,10)

exponential = 2^x

squared = x^2

par(mfrow = c(1,1))
plot(x, exponential, main = "Plot of a 2^x Function ", xlab = "Value of X", ylab = "The value of 2^x", type = "l")

plot(x, squared, main = "Plot of a x^2 Function ", xlab = "Value of X", ylab = "The value of x^2", type = "l")

```


```{r}
poke = read.csv(file = "pokemon.csv", header = TRUE, sep = ",")
head(poke)
names(poke)

plot(poke[,"Type_1"], horiz=TRUE,las=2)
```
Problem 4a)
```{r}
constraint1 = which(poke[,"Height_m"] > 2 & poke[, "isLegendary"] == 'True')
constraint1
```


Probelm 4b)
```{r}
constraints2 = which(poke[,"Body_Style"] == 'head_arms' | poke[,"Body_Style"] == 'serpentine_body')
constraints2
attack = constraints2[poke[,"Attack"]]
defense = constraints2[poke[,"Defense"]]

plot(attack, defense, main = "Attack vs Defense of 'Serpentine' or 'Head Arm' bodied pokemon", xlab = "Attack of the pokemon", ylab = "Defense of the pokemon", type = "p")
```
```{r}
```
pokenew = poke[1,]*NA
pokenew$Name = "Brian"
pokenew$Type_1 = "student"
pokemonextra = rbind(pokenew,poke)

is.data.frame(poke)

is.data.frame(pokemonextra)

is.numeric(poke[,"Type_1"])
is.numeric(pokemonextra[,"Type_1"])

is.factor(poke[,"Type_1"])

is.factor(pokemonextra[,"Type_1"])

poke[1:5,"Type_1"]
pokemonextra[1:5,"Type_1"]

unique(poke[,"Type_1"])
pokemonextra[,"Type_1"] = factor(pokemonextra[,"Type_1"])
pokemonextra[1:5, "Type_1"]

as.numeric(poke[, "Type_1"])
factor(poke[,"Attack"])

levels(pokemonextra[,"Type_1"])
levels(poke[,"Type_1"])

save.image(file="AllOfMyWorkSpace.Rdata")
save(poke,file="JustThePokeObject.Rdata")

```{r}
plot(poke[,"Attack"], poke[,"Defense"], ylab = "Defense", xlab = "Attack", col = poke[,"Generation"], pch = poke[,"Generation"], main = "Attack vs Defense \n of Different Generation Pokemon")

paste("generation",1:6)
legend(x=25,y=225,col=1:6,pch=1:6,paste("generation",1:6))

boxplot(poke[,"Attack"] ~ poke[,"Type_1"], main="Pokemon Attacks by Type_1",las=2)

boxplot(poke[,"HP"] ~ poke[,"Type_1"], main="Pokemon HP by Type_1",las=2)
```

```{r}
```
install.packages("RSQLite")
library(RSQLite)

```{r}
A = function(B)
{
  C = B + 7;
  return(C)
}
A(22)
```

Problem 5
```{r}
fibonnacci = function(n)
{
  if(n <= 1)
  {
    return(n)
  }
  else
  {
    return(fibonnacci(n-1) + fibonnacci(n-2))
  }
}
fibonnacci(20)
```