---
title: "lab2"
author: "Brian Panjaitan"
date: "25/01/2020"
output: html_document
---

```{r}
library(RSQLite)
library(DBI)

dbcon = dbConnect(SQLite(), dbname = "lab02.sqlite")
dbListTables(dbcon)

head(dbReadTable(dbcon, "zip"))
names(dbReadTable(dbcon, "zip"))
head(dbReadTable(dbcon, "POP2006"))
```

Question 1a)
The column names are zip_code, latitude, longitude, city, state, and country.

```{r}
tail(dbReadTable(dbcon, "CA"))
tail(dbReadTable(dbcon, "POP2011"))
tail(dbReadTable(dbcon, "POP2006"))
```
Question 1b)
The last 5 records in the data table 'CA' are
1636	1636	CA	S9V	Lloydminster	                    Saskatchewan	SK	53.2835	-110.0016	4
1637	1637	CA	S9X	Meadow Lake	                      Saskatchewan	SK	54.1335	-108.4347	4
1638	1638	CA	Y0A	Southeastern  Yukon (Watson Lake)	Yukon	        YT	61.5793	-131.1481	NA
1639	1639	CA	Y0B	Central Yukon (Dawson City)	      Yukon	        YT	64.6450	-137.5360	NA
1640	1640	CA	Y1A	Whitehorse	                      Yukon	        YT	60.7161	-135.0537	4

Question 1c)
The last 3 records in the data table 'POP2011' are
1635	Y0A	NA	1758	1090	782
1636	Y0B	NA	6538	4282	3028
1637	Y1A	NA	25601	10887	10307

Question 1d)
There are 1624 records in the data table 'POP2006'

```{r}
sql_qry_latlon = "SELECT * FROM zip WHERE Latitude > 55 AND Longitude < -140"
head(dbGetQuery(dbcon, sql_qry_latlon))
```
Question 2a)
There are 1596 records returned by this query
```{r}
sql_qry = "SELECT * FROM zip WHERE state == 'IL'"
head(dbGetQuery(dbcon, sql_qry))
tail(dbGetQuery(dbcon, sql_qry))
```
Exercise
sql_combine_qry = "SELECT * FROM tickets INNER JOIN zip ON tickets.zip_code = zip.zip_code"
head(dbGetQuery(dbcon, sql_combine_qry))

sql_combinePOP_qry = "SELECT * FROM POP2011 INNER JOIN POP2006 ON POP2011.Geographic_name = POP2006.Geographic_name"
head(dbGetQuery(dbcon, sql_combinePOP_qry))

sql_qry2  = "SELECT * FROM CA
              INNER JOIN POP2011 ON
                CA.Geographic_name =
                POP2011.Geographic_name
              WHERE
                Total_private_dwellings__2011 == 0"
join_eg  = dbGetQuery(dbcon, sql_qry2)
join_eg

Question 3a)
```{r}
sql_finelevel_qry = "SELECT latitude 
                      FROM zip INNER JOIN tickets 
                        ON zip.zip_code = tickets.zip_code
                      WHERE fine_level1_amount > 100"
join_eg2 = dbGetQuery(dbcon, sql_finelevel_qry)

group<-sample(1,64916,TRUE)
rowsum.data.frame(join_eg2, group, na.rm = TRUE)

B<-na.omit(join_eg2)
group<-sample(1,64876,TRUE)
rowsum.data.frame(B,group)
```


```{r}
library(rworldmap)
library(sp)
## ### Welcome to rworldmap ###
## For a short introduction type :  vignette(’rworldmap’)
library(rworldxtra)
worldmap = getMap(resolution = "high")
NrthAm = worldmap[which(worldmap$REGION=="North America"),]
plot(NrthAm, col = "white", bg = "lightblue",
  xlim = c(-140,-55), ylim = c(55,60))
```

```{r}
sql_popandca_query = "SELECT * FROM POP2006 INNER JOIN CA ON POP2006.Geographic_name = CA.Geographic_name WHERE Population__2006 < 32589"

join_eg3 = dbGetQuery(dbcon, sql_popandca_query)
join_eg3

plot(NrthAm, col = "white", bg = "lightblue", main = "Map of Locations in Canada with a population > 32589", xlab = "x-coordinates of location", ylab = "y-coordinates of location", xlim = c(-140,-55), ylim = c(55,60))

points(sql_popandca_query["longitude"], sql_popandca_query["latitude"], col = 'red', pch = 16)
```